---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

-----------------------------------------------------------------

## Loading and preprocessing the data
```{r}
df <- read.csv("activity.csv", sep = ",", header = TRUE)
#helpful time-formatting of intervals
interval_times <- seq(from=as.POSIXct("00:00",format="%H:%M"), to=as.POSIXct("23:55",format="%H:%M"), by=60*5)
```

## What is mean total number of steps taken per day?
```{r}
#find total, mean, median
total.steps <- tapply(df$steps, df$date, sum, na.rm = TRUE)
mean.steps <- signif(mean(total.steps, na.rm=TRUE),6)
med.steps <- median(total.steps, na.rm=TRUE)

#plot
hist(total.steps, xlab = "Daily number of steps", main = "Mean total number of steps taken per day", col ="HotPink")
```

- The mean number of total steps per day is `r mean.steps`.  
- The median number of total steps per day is `r med.steps`.  

## What is the average daily activity pattern?

```{r}
#find max interval
avg.steps.in.interval <- tapply(df$steps, df$interval, mean, na.rm = TRUE)
max.interval = which.max(avg.steps.in.interval)
max.interval.name = names(max.interval)

#plot
plot(y=avg.steps.in.interval, x=interval_times, type="l", xlab = "Interval time", ylab = "Average steps in interval", main = "Average daily activity pattern")
```

- The 5-minute interval which contains the maximum average number of steps is the interval at `r max.interval.name`. 

## Imputing missing values

```{r}
num.na <- sum(is.na(df$steps))
```

- The total number of missing values in the dataset is `r num.na`.

We will replace these missing values using the mean for the 5-minute interval.

```{r}
new.df <- df
```

## Are there differences in activity patterns between weekdays and weekends?
